A GRASP algorithm for the concrete delivery problem.

### 2023-08-17 Article/article.tex
save article

\documentclass{article}
% \documentclass[review]{elsarticle}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage[algo2e,noend]{algorithm2e}
\usepackage[compatible,noend]{algpseudocode}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage[table,xcdraw]{xcolor}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage{bbding}
\usepackage[english]{babel}
\usepackage{adjustbox}
\usepackage{tikz}
\usetikzlibrary{automata, topaths, calc, positioning, shapes, backgrounds, fit, matrix}
\usepackage{caption}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{datatool}
\usepackage{array}
\usepackage{pgfplotstable}
\pgfplotsset{width=7cm,compat=newest}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{capt-of}
\usepackage{multirow}
\usepackage{float}
\usepackage[text={15cm,21cm},centering]{geometry}
\usepackage{setspace}
\usepackage{array}
\allowdisplaybreaks
\usepackage{lineno}
\usepackage{tkz-graph}
\usepackage{breqn}
\tikzset{
base/.style = {shape=rectangle, 
                      anchor=center,minimum size=5mm, 
                     align=center,
                     top color=white, ,inner sep=0ex,
                     minimum size=5mm
                     },
    LC11/.style =   {  base,   
                    text width=3em, 
                    bottom color=brown!100,
                    },
    UC11/.style = {     base,    
                    text width=5em, 
                    bottom color=brown!100,
                    align = right,
                },
    LC12/.style =   {  base,   
                    text width=1em, 
                    bottom color=orange!100,
                    },
    UC12/.style = {     base,    
                    text width=2.5em, 
                    bottom color=orange!100,
                },
    LC21/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=brown!100,
                    },
    UC21/.style = {     base,    
                    text width=3.5em, 
                    bottom color=brown!100,
                },
    LC22/.style =   {  base,   
                    text width=4em, 
                    bottom color=blue!100,
                    },
    UC22/.style = {     base,    
                    text width=7em, 
                    bottom color=blue!100,
                    align = left,
                },
    UC221/.style = {     base,    
                    text width=3.5em, 
                    bottom color=blue!100,
                    % color=blue!100,
                    outer xsep=0em,
                    % align = right,
                },
                UC231/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=blue!100,
                    },
    LC23/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=orange!100,
                    },
    UC23/.style = {     base,    
                    text width=2.em, 
                    bottom color=orange!100,
                },
  env/.style      = {base, font=\ttfamily\normalsize},
label/.style   = {base,font=\ttfamily\normalsize, text width = 8em, 
  inner sep=0em, rounded corners=1mm,bottom color=red!80,},
  dummy/.style    = {circle,draw}
}

@@

The GRASP algorithm, proposed by \cite{feo1989probabilistic}, is a two-phase iterative suite consisting of constructive and local search algorithms. In the construction phase, a feasible solution $S$ is generated using a greedy randomized algorithm. Then, a local search algorithm explores the neighborhood of $S$ to identify a local optimum. Algorithm~\ref{alg_grasp} outlines the pseudocode of the GRASP algorithm. To avoid redundant computations, a hash table $H$ is used to ensure that the local search is not applied multiple times to the same solution.  The procedure stops and returns the best overall solution when certain stopping conditions, such as reaching a time limit or a maximum number of iterations, are met. In our implementation, we also add a path relinking procedure that uses information about previous solutions to improve the search process.

    {\setstretch{1.0}
        {\small
        \begin{algorithm}[hpt]
            \caption{Pseudo-code of the GRASP algorithm }
            \label{alg_grasp}
            \DontPrintSemicolon
            \LinesNumbered
            \setcounter{AlgoLine}{0}
            % \KwIn{ \textit{H}: List of constructive greedy randomized heuristics }
            \KwIn{ $\phi$: number of iterations before path relinking }
            $S^* \leftarrow \emptyset$    \hspace{2mm} $T \leftarrow \emptyset$       $Cost(S^*) \leftarrow \infty$

@@

            $counter \leftarrow  0$

@@

                $T \leftarrow T \cup \{S\}$

@@

                \uIf{$counter \text{ } mod \text{ } \phi == 0$}{
                    $S^* \leftarrow PathRelinking(T)$

                    $T \leftarrow \emptyset$
                }

                $counter \leftarrow counter + 1$

@@

    {\setstretch{1}
        %  {\small
        \begin{algorithm}[]
            \caption{Customer-Based insertion algorithm }
            \label{alg:greedyCustIns}
            \DontPrintSemicolon
            \LinesNumbered
            \setcounter{AlgoLine}{0}
            \KwIn{  $S$: empty solution $S$, $K$: vehicles set \hspace{15mm} \\$\Pi$: custom sorted customers list }

@@

    {\setstretch{1}
        %  {\small
        \begin{algorithm}[H]
            \caption{Delivery-based insertion algorithm }
            \label{alg:delbasedIns}
            \DontPrintSemicolon
            \LinesNumbered
            \setcounter{AlgoLine}{0}
            \KwIn{  $S$: empty solution $S$}

@@

\subsection{Path relinking}

After the construction and local search steps, it is possible that some customers remain unscheduled in one solution while being accommodated in another. The goal of the path relinking procedure is to use each customer's scheduling information from existing solutions and combine them effectively to construct a solution that schedules all customers. This algorithm iterates through each element of a pool of solutions and attempts to insert each customer's schedule into a newly constructed solution.

@@

\subsection{Generation of instances}
\newcommand{\nbInstance}{36}
The dataset used in this section was obtained from our partner and contains records representing delivery operations from up to 8 production centers over a period of $\nbInstance$ days. We have created $\nbInstance$ instances, where each instance corresponds to a daily operation. An instance contains information such as each driver's capacity, associated batch plant, and shift start time. For each customer, we have the due time, the total demand, and the number of orders (type of concrete) received. For each order, we have its demand and associated production plant. Finally, we have the loading capacity for each plant. The name of an instance has the format $C\_k\_n\_o\_z$, where $k$ is the number of available drivers, $n$ is the number of customers, $o$ is the total number of daily orders, and $z$ is the number of plants. The dataset is divided into small, medium, and large sets according to the total number of daily orders. We have summarized the dataset in the Table~\ref{tab:instances}.

\begin{table}[htpb]
    \centering
    \caption{Instances summary}
    \label{tab:instances}
    \resizebox*{0.8\textwidth}{!}{
    \begin{tabular}{lcccccc}
        \toprule
        {} &  \# &         Demand  &   \#Order & \#Client &  \#Driver & \#Depot \\
          &       &         (m$^3$)        &         &         &          &        \\
        \midrule
        Small  &     8 &    226.5-937.5 &     7-14 &    4-11 &    13-35 &    1-3 \\
        Medium &    14 &  1,160.5-2,971.0 &    43-98 &   40-89 &   76-137 &    6-8 \\
        Large  &    14 &  3,078.5-3,953.5 &  107-136 &  92-127 &  129-150 &    8 \\
        \bottomrule
        \end{tabular}  
    }
\end{table}

@@

\begin{table}[htbp]
    \centering
    \caption{Performance of the GRASP heuristic on the CDP benchmark instances}
    \label{tab:cdp_instances}
    \resizebox{1\textwidth}{!}{
    \begin{tabular}{@{}cccccccccccc@{}}
    \toprule
     &  & \multicolumn{2}{c}{CP} & \multicolumn{2}{c}{MIP} & \multicolumn{2}{c}{SD-heuristic} & \multicolumn{2}{c}{Hybrid} & \multicolumn{2}{c}{GRASP} \\ \cmidrule(l){3-10} \cmidrule(l){11-12} 
     &  & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) \\ \cmidrule(l){3-10} \cmidrule(l){11-12} 
    \multirow{2}{*}{Set A} & Avg & 4.2 & 197,012 & 7.3 & 13,405,798 & 9.1 & 23 & 7.0 & 100,765 & 5.7 & 13,186 \\ \cmidrule(l){2-10} \cmidrule(l){11-12} 
     & Opt & \multicolumn{2}{c}{40/64} & \multicolumn{2}{c}{37/64} & \multicolumn{2}{c}{30/64} & \multicolumn{2}{c}{35/64} & \multicolumn{2}{c}{35/64} \\ \cmidrule(l){3-10} \cmidrule(l){11-12} 
     \multirow{2}{*}{Set B} & Avg & 12.1 & 357,313 & - & - & 16.3 & 1,331 & - & - & 13.8 & 574,983\\ \cmidrule(l){2-10} \cmidrule(l){11-12} 
     & Opt & \multicolumn{2}{c}{55/128} & \multicolumn{2}{c}{-} & \multicolumn{2}{c}{40/128} & \multicolumn{2}{c}{-} & \multicolumn{2}{c}{44/128} \\ \bottomrule
    \end{tabular}
    }
\end{table}

@@

\begin{table}[htpb]
    \centering
    \caption{Parameters of the real-world instances}
    \label{tab:problem_parameters}
%    \resizebox*{\textwidth}{!}{
    \begin{tabularx}{\textwidth}{Xr}
        \toprule
        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Value} \\ \midrule
        Unloading duration ($\tau_c^u$) & 2 min$/m^3$ \\
        Cleaning duration ($\rho$) & 10 min \\
        Adjustment duration ($\alpha$) & 10 min \\
        Max travel time ($\Delta$) & 120 min \\
        Min working time ($M_T$) & 180 min \\
        Max working time ($N_T$) & 480 min \\
        Max overtime duration ($O_T$) & 120 min \\
        Max delay between two consecutive deliveries of the same order ($\gamma^1$) & 20 min \\
        Max delay between two consecutive deliveries of different orders ($\gamma^2)$ & 25 min \\
    %    $\beta_1$ & 10000  \\
    %    $\beta_2$ & 10000  \\
    %    $\beta_3$ & 1000  \\
    %    $\beta_4$ & 100  \\
        \bottomrule
    \end{tabularx}
%    }
\end{table}

@@

\begin{table}[htbp]
    \centering
    \caption{RMC delivered within different runtimes}
    \label{tab:runtime}
    \resizebox*{0.5\textwidth}{!}{
        \begin{tabular}{llcccc}
            \toprule
            &  &      \multicolumn{4}{c}{Runtime (min)} \\
            \cmidrule{3-6}
            & &      5   & 10  &  30  & 60  \\
            %  & {} &         &         &        &        \\
            \midrule
            \multirow{1}{*}{Small} & \% Load &  100.00 &  100.00 &  100.0 &  100.0 \\
                %   & \# instances &    8 &    8 &    8 &    8 \\
            \cmidrule{2-6}
                  \multirow{1}{*}{Medium} & \% Load &   99.86 &   99.86 &  100.0 &  100.0 \\
                %   & \# instances &   13 &   13 &   14 &   14 \\
                  \cmidrule{2-6}
                  \multirow{1}{*}{Large} & \% Load &   99.79 &   99.93 &  100.0 &  100.0 \\
                %   & \# instances &   12 &   13 &   14 &   14 \\
            \bottomrule
            \end{tabular} 
    }

@@

Table \ref*{tab:results_grasp_ls} shows the detailed results for each instance. The runtime is set to 3600 seconds. The table reports the requirements of each instance, the components of the objective function, the number of drivers used, and the execution time in seconds.
%  the travel cost ($TC$), the penalties associated with unfulfilled orders ($PUO$), the sum of the first delivery delays ($FDD$) for each customer, the sum of the driver underutilization costs ($DUC$) and driver overtime costs ($DOC$).

@@

\begin{table}[htbp]

>>>>

\documentclass{article}
% \documentclass[review]{elsarticle}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage[algo2e,noend]{algorithm2e}
\usepackage[compatible,noend]{algpseudocode}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage[table,xcdraw]{xcolor}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage{bbding}
\usepackage[english]{babel}
\usepackage{adjustbox}
\usepackage{tikz}
\usepackage{subcaption}
\usetikzlibrary{automata, topaths, calc, positioning, shapes, backgrounds, fit, matrix}
\usepackage{caption}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{datatool}
\usepackage{array}
\usepackage{pgfplotstable}
\pgfplotsset{width=7cm,compat=newest}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{capt-of}
\usepackage{multirow}
\usepackage{float}
\usepackage[text={15cm,21cm},centering]{geometry}
\usepackage{setspace}
\usepackage{array}
\allowdisplaybreaks
\usepackage{lineno}
\usepackage{tkz-graph}
\usepackage{breqn}
\tikzset{
base/.style = {shape=rectangle, 
                      anchor=center,minimum size=5mm, 
                     align=center,
                     top color=white, ,inner sep=0ex,
                     minimum size=5mm
                     },
    LC11/.style =   {  base,   
                    text width=3em, 
                    bottom color=brown!100,
                    },
    UC11/.style = {     base,    
                    text width=5em, 
                    bottom color=brown!100,
                    align = right,
                },
    LC12/.style =   {  base,   
                    text width=1em, 
                    bottom color=orange!100,
                    },
    UC12/.style = {     base,    
                    text width=2.5em, 
                    bottom color=orange!100,
                },
    LC21/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=brown!100,
                    },
    UC21/.style = {     base,    
                    text width=3.5em, 
                    bottom color=brown!100,
                },
    LC22/.style =   {  base,   
                    text width=4em, 
                    bottom color=blue!100,
                    },
    UC22/.style = {     base,    
                    text width=7em, 
                    bottom color=blue!100,
                    align = left,
                },
    UC221/.style = {     base,    
                    text width=3.5em, 
                    bottom color=blue!100,
                    % color=blue!100,
                    outer xsep=0em,
                    % align = right,
                },
                UC231/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=blue!100,
                    },
    LC23/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=orange!100,
                    },
    UC23/.style = {     base,    
                    text width=2.em, 
                    bottom color=orange!100,
                },
  env/.style      = {base, font=\ttfamily\normalsize},
label/.style   = {base,font=\ttfamily\normalsize, text width = 8em, 
  inner sep=0em, rounded corners=1mm,bottom color=red!80,},
  dummy/.style    = {circle,draw}
}

@@

The GRASP algorithm, proposed by \cite{feo1989probabilistic}, is a two-phase iterative suite consisting of constructive and local search algorithms. In the construction phase, a feasible solution $S$ is generated using a greedy randomized algorithm. Then, a local search algorithm explores the neighborhood of $S$ to identify a local optimum. Algorithm~\ref{alg_grasp} outlines the pseudocode of the GRASP algorithm. To avoid redundant computations, a hash table $H$ is used to ensure that the local search is not applied multiple times to the same solution.  The procedure stops and returns the best overall solution when certain stopping conditions, such as reaching a time limit or a maximum number of iterations, are met. %In our implementation, we also add a path relinking procedure that uses information about previous solutions to improve the search process.

    {\setstretch{1.0}
        {\small
        \begin{algorithm}[hbpt]
            \caption{Pseudo-code of the GRASP algorithm }
            \label{alg_grasp}
            \DontPrintSemicolon
            \LinesNumbered
            \setcounter{AlgoLine}{0}
            % \KwIn{ \textit{H}: List of constructive greedy randomized heuristics }
            \KwIn{ $\phi$: number of iterations before path relinking }
            $S^* \leftarrow \emptyset$    \hspace{2mm} $T \leftarrow \emptyset$       $Cost(S^*) \leftarrow \infty$

@@

            % $counter \leftarrow  0$

@@

                % $T \leftarrow T \cup \{S\}$

@@

                % \uIf{$counter \text{ } mod \text{ } \phi == 0$}{
                %     $S^* \leftarrow PathRelinking(T)$

                %     $T \leftarrow \emptyset$
                % }

                % $counter \leftarrow counter + 1$

@@

    {\setstretch{1}
        %  {\small
        \begin{algorithm}[htpb]
            \caption{Customer-Based insertion algorithm }
            \label{alg:greedyCustIns}
            \DontPrintSemicolon
            \LinesNumbered
            \setcounter{AlgoLine}{0}
            \KwIn{  $S$: empty solution $S$, $K$: vehicles set \hspace{15mm} \\$\Pi$: custom sorted customers list }

@@

    {\setstretch{1}
        %  {\small
        \begin{algorithm}[htb]
            \caption{Delivery-based insertion algorithm }
            \label{alg:delbasedIns}
            \DontPrintSemicolon
            \LinesNumbered
            \setcounter{AlgoLine}{0}
            \KwIn{  $S$: empty solution $S$}

@@

% \subsection{Path relinking}

% After the construction and local search steps, it is possible that some customers remain unscheduled in one solution while being accommodated in another. The goal of the path relinking procedure is to use each customer's scheduling information from existing solutions and combine them effectively to construct a solution that schedules all customers. This algorithm iterates through each element of a pool of solutions and attempts to insert each customer's schedule into a newly constructed solution.

@@

\subsection{Generation of instances}
\newcommand{\nbInstance}{36}
The dataset used in this section was obtained from our partner and contains records representing delivery operations from up to 8 production centers over a period of $\nbInstance$ days. We have created $\nbInstance$ instances, where each instance corresponds to a daily operation. An instance contains information such as each driver's capacity, associated batch plant, and shift start time. For each customer, we have the due time, the total demand, and the number of orders (type of concrete) received. For each order, we have its demand and associated production plant. Finally, we have the loading capacity for each plant. The name of an instance has the format $C\_k\_n\_o\_z$, where $k$ is the number of available drivers, $n$ is the number of customers, $o$ is the total number of daily orders, and $z$ is the number of plants. The dataset is divided into small, medium, and large sets according to the total number of daily orders. We have summarized the dataset in Table~\ref{tab:instances}.

\begin{table}[htpb]
    \centering
    \caption{Instances summary}
    \label{tab:instances}
    \small
    \resizebox*{0.8\textwidth}{!}{
    \begin{tabular}{lcccccc}
        \toprule
        {} &  \# &         Demand  &   \#Order & \#Client &  \#Driver & \#Depot \\
          &       &         (m$^3$)        &         &         &          &        \\
        \midrule
        Small  &     8 &    226.5 - 937.5 &     7 - 14 &    4 - 11 &    13-35 &    1-3 \\
        Medium &    14 &  1,160.5 - 2,971.0 &    43 - 98 &   40 - 89 &   76-137 &    6-8 \\
        Large  &    14 &  3,078. - 3,953.5 &  107 - 136 &  92 - 127 &  129-150 &    8 \\
        \bottomrule
        \end{tabular}  
    }
\end{table}

@@

\begin{table}[htbp]
    \centering
    \caption{Performance of the GRASP heuristic on the CDP benchmark instances}
    \label{tab:cdp_instances}
    \scriptsize
    \resizebox{1\textwidth}{!}{
    \begin{tabular}{@{}cccccccccccc@{}}
    \toprule
     &  & \multicolumn{2}{c}{CP} & \multicolumn{2}{c}{MIP} & \multicolumn{2}{c}{SD-heuristic} & \multicolumn{2}{c}{Hybrid} & \multicolumn{2}{c}{GRASP} \\ \cmidrule(l){3-10} \cmidrule(l){11-12} 
     &  & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) \\ \cmidrule(l){3-10} \cmidrule(l){11-12} 
    \multirow{2}{*}{Set A} & Avg & 4.2 & 197,012 & 7.3 & 13,405,798 & 9.1 & 23 & 7.0 & 100,765 & 5.7 & 13,186 \\ \cmidrule(l){2-10} \cmidrule(l){11-12} 
     & Opt & \multicolumn{2}{c}{40/64} & \multicolumn{2}{c}{37/64} & \multicolumn{2}{c}{30/64} & \multicolumn{2}{c}{35/64} & \multicolumn{2}{c}{35/64} \\ \cmidrule(l){3-10} \cmidrule(l){11-12} 
     \multirow{2}{*}{Set B} & Avg & 12.1 & 357,313 & - & - & 16.3 & 1,331 & - & - & 13.8 & 574,983\\ \cmidrule(l){2-10} \cmidrule(l){11-12} 
     & Opt & \multicolumn{2}{c}{55/128} & \multicolumn{2}{c}{-} & \multicolumn{2}{c}{40/128} & \multicolumn{2}{c}{-} & \multicolumn{2}{c}{44/128} \\ \bottomrule
    \end{tabular}
    }
\end{table}

@@

\begin{table}[hbt]
    \centering
    \caption{Parameters of the real-world instances}
    \label{tab:problem_parameters}
    \small
%    \resizebox*{\textwidth}{!}{
    \begin{tabularx}{\textwidth}{Xr}
        \toprule
        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Value} \\ \midrule
        Unloading duration ($\tau_c^u$) & 2 min$/m^3$ \\
        Cleaning duration ($\rho$) & 10 min \\
        Adjustment duration ($\alpha$) & 10 min \\
        Max travel time ($\Delta$) & 120 min \\
        Min working time ($M_T$) & 180 min \\
        Max working time ($N_T$) & 480 min \\
        Max overtime duration ($O_T$) & 120 min \\
        Max delay between two consecutive deliveries of the same order ($\gamma^1$) & 20 min \\
        Max delay between two consecutive deliveries of different orders ($\gamma^2)$ & 25 min \\
       $\beta_1$ & 10,0000  \\
       $\beta_2$ & 1,0000  \\
       $\beta_3$ & 30  \\
       $\beta_4$ & 20  \\
        \bottomrule
    \end{tabularx}
%    }
\end{table}

@@

\begin{table}[htb]
    \centering
    \caption{RMC delivered within different runtimes}
    \label{tab:runtime}
    \scriptsize
    \resizebox*{0.8\textwidth}{!}{
        \begin{tabular}{llccccc}
            \toprule
            &  &      \multicolumn{5}{c}{Runtime (min)} \\
            \cmidrule{3-7}
                  &  &      1  &      5  &      10 &     30 &     60 \\
            \midrule
            \multirow{2}{*}{Small}  & \%Load &  100.00 &  100.00 &  100.00 &  100.0 &  100.0 \\
                  & \#Instance &    8 &    8 &    8 &    8 &    8 \\
                  \cmidrule{2-7}
            \multirow{2}{*}{Medium}  & \%Load &   99.71 &   99.93 &   99.86 &  100.0 &  100.0 \\
                  & \#Instance &   11 &   13 &   13 &   14 &   14 \\
                  \cmidrule{2-7}
            \multirow{2}{*}{Large}  & \%Load &   99.64 &   99.64 &   99.79 &  100.0 &  100.0 \\
                  & \#Instance &   10 &   10 &   12 &   14 &   14 \\
            \bottomrule
            \end{tabular}
    }

@@

Table \ref*{tab:all_instances} shows the detailed results for each instance. The runtime is set to 3600 seconds. The table reports the requirements of each instance, the components of the objective function, the number of drivers used, and the execution time in seconds.
%  the travel cost ($TC$), the penalties associated with unfulfilled orders ($PUO$), the sum of the first delivery delays ($FDD$) for each customer, the sum of the driver underutilization costs ($DUC$) and driver overtime costs ($DOC$).

@@

\begin{table}[htb]
    \centering
    \label{tab:all_instances}
    \resizebox*{1.2\textwidth}{!}{
    \begin{tabular}{llrrrrrrrrrrrrrrrrrr}
         &  & \multicolumn{18}{c}{Best} \\
         &  & Demand & $TC$ & $FDD$ & $mFDD$ & $DUC$ & $DOC$ & $Z$ & \#K & Time & $TC$ & $FDD$ & $mFDD$ & $DUC$ & $DOC$ & Z & \#K & $PUO$ & Time \\
         &  & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) & (min) \\
        size & Instance &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
        \multirow[c]{8}{*}{Small} & C_13_11_12_1 & 226.50 & 1,243.55 & 0.00 & 0.00 & 0.00 & 0.00 & 1,243.55 & 13 & 60.34 & 1,243.55 & 0.00 & 0.00 & 37.68 & 0.00 & 2,373.86 & 13.00 & 0.00 & 60.23 \\
         & C_13_5_8_1 & 267.00 & 745.10 & 0.00 & 0.00 & 0.00 & 0.00 & 745.10 & 13 & 60.28 & 745.10 & 0.00 & 0.00 & 0.00 & 0.00 & 745.10 & 13.00 & 0.00 & 60.29 \\
         & C_18_6_11_2 & 333.50 & 753.26 & 0.00 & 0.00 & 125.33 & 0.00 & 4,513.25 & 18 & 60.21 & 753.26 & 0.00 & 0.00 & 194.68 & 0.00 & 6,593.74 & 18.00 & 0.00 & 60.27 \\
         & C_15_4_7_2 & 375.00 & 1,014.25 & 0.00 & 0.00 & 172.13 & 76.10 & 7,700.13 & 15 & 60.39 & 1,014.93 & 0.00 & 0.00 & 132.77 & 291.65 & 10,830.80 & 15.00 & 0.00 & 60.37 \\
         & C_19_7_8_2 & 388.00 & 1,745.83 & 0.00 & 0.00 & 224.47 & 87.86 & 10,237.08 & 19 & 60.21 & 1,765.51 & 0.00 & 0.00 & 314.77 & 150.86 & 14,225.62 & 18.60 & 0.00 & 60.21 \\
         & C_29_10_14_3 & 613.50 & 3,628.79 & 49.18 & 18.77 & 112.94 & 547.16 & 67,145.19 & 29 & 60.88 & 3,741.98 & 48.61 & 21.45 & 210.99 & 735.59 & 73,392.66 & 28.40 & 0.00 & 60.65 \\
         & C_31_8_11_3 & 776.00 & 2,297.20 & 0.00 & 0.00 & 606.66 & 566.96 & 31,836.07 & 30 & 61.06 & 2,330.55 & 0.00 & 0.00 & 781.61 & 656.53 & 38,909.59 & 29.40 & 0.00 & 60.56 \\
         & C_35_9_10_3 & 937.50 & 4,174.37 & 0.00 & 0.00 & 221.69 & 1,161.60 & 34,056.98 & 35 & 61.27 & 4,175.30 & 0.00 & 0.00 & 341.84 & 1,329.53 & 41,021.00 & 34.40 & 0.00 & 60.96 \\
        \multirow[c]{14}{*}{Medium} & C_76_40_43_6 & 1,160.50 & 5,967.04 & 6.18 & 3.48 & 2,961.59 & 644.42 & 113,884.73 & 71 & 60.24 & 6,311.56 & 17.24 & 9.45 & 3,014.61 & 705.95 & 128,106.36 & 67.80 & 0.00 & 60.38 \\
         & C_104_42_47_8 & 1,565.00 & 9,777.47 & 32.02 & 13.04 & 2,829.97 & 240.64 & 131,507.57 & 98 & 60.30 & 9,358.19 & 34.11 & 20.52 & 3,890.10 & 678.98 & 173,754.55 & 94.40 & 0.00 & 60.26 \\
         & C_94_63_70_7 & 1,746.50 & 14,428.70 & 78.89 & 19.26 & 1,147.89 & 1,464.35 & 157,038.10 & 94 & 60.52 & 14,369.08 & 90.19 & 24.90 & 1,353.87 & 1,391.38 & 173,007.04 & 93.20 & 0.00 & 60.45 \\
         & C_116_67_78_8 & 1,839.50 & 13,871.90 & 67.25 & 33.18 & 2,347.71 & 523.28 & 162,021.52 & 114 & 60.28 & 13,602.88 & 67.90 & 32.59 & 2,419.36 & 857.33 & 171,229.15 & 113.60 & 0.00 & 60.36 \\
         & C_116_71_82_8 & 2,060.00 & 12,089.70 & 147.66 & 27.17 & 1,966.01 & 922.73 & 237,183.56 & 116 & 60.30 & 12,678.16 & 158.64 & 35.84 & 1,991.31 & 1,125.75 & 253,575.07 & 114.20 & 0.00 & 60.26 \\
         & C_117_57_70_6 & 2,327.50 & 15,153.30 & 114.16 & 22.20 & 1,823.68 & 1,671.48 & 217,448.30 & 117 & 60.45 & 15,495.00 & 142.42 & 34.52 & 1,388.61 & 1,680.45 & 233,181.42 & 117.00 & 0.00 & 60.39 \\
         & C_137_79_83_7 & 2,425.00 & 18,360.30 & 335.15 & 34.20 & 2,552.72 & 1,794.17 & 465,977.30 & 135 & 60.26 & 18,960.44 & 375.76 & 48.60 & 2,124.67 & 1,857.88 & 495,614.54 & 135.60 & 0.00 & 60.43 \\
         & C_127_66_80_8 & 2,512.50 & 17,599.10 & 14.37 & 5.00 & 1,046.33 & 1,242.32 & 88,203.50 & 126 & 60.15 & 16,033.26 & 10.42 & 3.60 & 1,579.58 & 1,552.10 & 104,879.09 & 125.40 & 0.00 & 60.26 \\
         & C_128_68_74_7 & 2,595.00 & 18,728.80 & 191.00 & 42.50 & 1,418.80 & 2,841.15 & 309,116.80 & 127 & 60.36 & 19,774.38 & 361.55 & 49.14 & 944.63 & 2,616.67 & 461,998.19 & 127.80 & 0.00 & 60.61 \\
         & C_136_85_97_8 & 2,673.00 & 18,894.60 & 137.37 & 48.57 & 1,155.58 & 2,137.00 & 233,669.00 & 134 & 60.71 & 18,223.56 & 188.51 & 46.67 & 2,134.46 & 2,352.19 & 317,811.36 & 131.40 & 0.00 & 60.48 \\
         & C_128_78_85_8 & 2,685.50 & 18,041.60 & 192.36 & 35.71 & 1,374.29 & 3,234.19 & 316,314.10 & 127 & 60.68 & 18,463.86 & 305.84 & 39.44 & 1,277.34 & 3,156.96 & 425,759.26 & 127.20 & 0.00 & 60.37 \\
         & C_131_77_85_8 & 2,893.50 & 18,063.00 & 200.24 & 43.22 & 780.69 & 1,539.10 & 272,509.58 & 131 & 60.23 & 18,003.00 & 212.58 & 47.46 & 1,248.71 & 1,716.14 & 302,370.43 & 129.60 & 0.00 & 60.41 \\
         & C_137_89_97_7 & 2,939.50 & 22,038.10 & 438.27 & 58.56 & 849.81 & 3,461.14 & 555,029.11 & 137 & 60.33 & 23,293.04 & 636.01 & 56.14 & 849.88 & 3,523.86 & 755,280.53 & 137.00 & 0.00 & 60.47 \\
         & C_133_84_98_7 & 2,971.00 & 20,992.60 & 1,061.17 & 59.39 & 546.11 & 2,742.51 & 1,153,396.07 & 133 & 60.30 & 22,000.05 & 1,157.60 & 59.25 & 805.41 & 2,291.38 & 1,249,585.08 & 133.00 & 18.70 & 60.67 \\
        \multirow[c]{14}{*}{Large} & C_132_98_109_8 & 3,078.50 & 23,425.80 & 160.94 & 29.44 & 493.20 & 4,426.10 & 287,683.71 & 132 & 60.40 & 23,469.12 & 247.44 & 31.77 & 548.73 & 4,162.33 & 370,622.52 & 131.80 & 0.00 & 60.51 \\
         & C_129_101_119_8 & 3,229.00 & 19,453.30 & 166.74 & 35.78 & 1,138.10 & 4,719.55 & 314,728.30 & 129 & 60.31 & 19,051.68 & 268.97 & 40.76 & 1,232.06 & 3,820.36 & 401,387.86 & 129.00 & 0.00 & 60.45 \\
         & C_141_114_136_8 & 3,350.50 & 21,863.20 & 943.94 & 55.35 & 1,177.01 & 2,513.42 & 1,051,386.90 & 141 & 60.36 & 21,505.60 & 1,127.23 & 57.20 & 1,422.68 & 2,339.21 & 1,238,202.03 & 141.00 & 8.70 & 60.58 \\
         & C_140_114_132_8 & 3,401.50 & 23,969.70 & 988.55 & 54.37 & 981.26 & 3,253.14 & 1,107,019.45 & 140 & 60.55 & 23,938.44 & 1,055.09 & 54.86 & 910.17 & 3,269.09 & 1,171,715.10 & 139.80 & 0.00 & 60.68 \\
         & C_143_101_123_8 & 3,437.50 & 26,284.90 & 335.48 & 43.51 & 566.06 & 3,912.96 & 457,006.99 & 143 & 60.80 & 25,711.02 & 352.25 & 46.32 & 902.98 & 4,085.07 & 486,754.99 & 143.00 & 0.00 & 60.54 \\
         & C_137_112_129_8 & 3,471.00 & 22,338.30 & 275.09 & 45.62 & 375.23 & 3,819.75 & 385,076.08 & 137 & 60.76 & 22,562.40 & 340.81 & 49.10 & 402.39 & 3,371.09 & 442,869.08 & 137.00 & 0.00 & 60.82 \\
         & C_142_114_129_8 & 3,499.50 & 22,387.60 & 654.63 & 55.27 & 1,090.38 & 4,472.55 & 799,184.00 & 142 & 60.58 & 22,478.28 & 800.95 & 57.01 & 1,294.76 & 4,168.21 & 945,633.44 & 141.60 & 0.00 & 61.20 \\
         & C_149_98_122_8 & 3,513.00 & 21,224.70 & 684.52 & 51.12 & 2,267.63 & 3,046.60 & 834,708.60 & 148 & 61.18 & 20,767.50 & 778.44 & 54.95 & 2,236.93 & 2,852.20 & 923,357.90 & 147.75 & 3.00 & 60.77 \\
         & C_139_98_108_8 & 3,541.00 & 22,043.20 & 522.32 & 51.62 & 482.79 & 3,648.54 & 631,819.76 & 139 & 61.46 & 21,613.40 & 661.04 & 55.50 & 852.30 & 3,716.15 & 782,546.76 & 138.60 & 0.00 & 61.16 \\
         & C_144_108_122_8 & 3,670.50 & 25,806.90 & 675.42 & 50.38 & 548.50 & 3,209.16 & 781,866.07 & 144 & 60.38 & 24,738.28 & 746.03 & 56.42 & 664.90 & 3,465.76 & 860,025.70 & 144.00 & 0.00 & 61.69 \\
         & C_142_92_107_8 & 3,684.50 & 23,586.40 & 182.64 & 24.02 & 802.97 & 4,396.54 & 318,243.24 & 142 & 60.40 & 24,553.30 & 298.65 & 38.73 & 644.19 & 4,423.61 & 431,001.04 & 142.00 & 0.00 & 60.47 \\
         & C_138_114_136_8 & 3,739.50 & 23,639.00 & 600.38 & 55.18 & 1,230.76 & 5,313.96 & 767,223.00 & 137 & 60.16 & 25,366.94 & 791.53 & 54.14 & 668.63 & 5,501.79 & 946,993.86 & 137.20 & 0.00 & 60.90 \\
